Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidic System

### 2022-12-10 paper-kelompok/main.tex
fixed accuracy analysis

The biggest error factor for transmittance was the shift in the baseline.
The device measured numerous instances of negative absorbance.
A negative absorbance is the result of a transmittance higher than 100\%; the blank intensity readout was higher than the sample intensity readout.
In other words, the sensor deemed the blank (water) brighter than the sample.
This could happen when the intensity from the light source was brighter for the sample than the blank.
The voltage log confirmed this hypothesis.
A blank measurement took longer time than a sample measurement.
The longer a measurement took, the lower the power dropped, and the lower intensity was readout.

>>>>

The biggest error factor for transmittance was the shift in the baseline.
The device measured numerous instances of negative absorbance.
A negative absorbance is the result of a transmittance higher than 100\%.
Transmittance is defined as $T=I_{sample}/I_{blank}$, which means the blank intensity readout was lower than the sample intensity readout.
In other words, the sensor deemed the blank (water) darker than the sample.
This could happen when the intensity from the light source was darker for the blank than the sample.
The voltage log confirmed this hypothesis.
A blank measurement took longer time than a sample measurement.
The longer a measurement took time, the lower the power dropped, and the lower the intensity was read.
